### 2018-02-25 DASFAA_2018/CR/Gruba_final/02-overview.tex

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$. Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
\end{definition}

>>>>

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either \twd{} or \retd{}), the generated time $T$ of $M_b$, the message content $M$, and $flag$ denoting $M_b$ is \retd{} or originally \tw{} by $O$. Here we use 1 and 0 to denote \retd{} and  \tw{}, respectively.
\end{definition}

### 2018-02-25 DASFAA_2018/CR/Gruba_final/03-fe.tex

\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twg{} microblogs is within 1 min. Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).

@@

If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic) $\gamma$.
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

>>>>

\sstab(e) the normalized vectors with respect to the gap distribution of a user's \retg{}/\twg{} behavior: $P_{rg,u}\ = (p''_{r0},\ p''_{r1},\ ...,\ p''_{r5})$, $P_{tg,u}\ = (p''_{t0},\ p''_{t1},\ ...,\ p''_{t5})$, in which $p''_{r0}$/$p''_{t0}$ is the probability that the gap between two \retd{}/\twd{} microblogs is within 1 min. Ditto for $p''_{r1}$/$p''_{t1}$ (1 min to 1 hour), $p''_{r2}$/$p''_{t2}$ (1 to 12 hours), $p''_{r3}$/$p''_{t3}$ (12 to 24 hours), $p''_{r4}$/$p''_{t4}$ (24 to 48 hours) and  $p''_{r5}$/$p''_{t5}$ (more than 48 hours).

@@

If $sim(b, \gamma)$ satisfies a certain threshold (3 by default), topic $\gamma$ is labeled to microblog $b$;
the user $u$ is then discovered having an explicit interest (topic $\gamma$).
Thus, by looking into the similarity of $b$ against all topics in lexicon $L$, the explicit interests of $u$ is derived, in the form of interest feature (see Definition \ref{def:inte}).

### 2018-02-25 DASFAA_2018/CR/Gruba_final/06-perf.tex

\par In this section, we shall first detail the experimental setting, and we then present the evaluation result and analysis, showing the benefit of \sys{} against state of the art approaches.

@@

\subsection{Result and Analysis}
Next, we shall report the performance of system \sys{} over each component.

@@

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:10-c} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

@@

\begin{figure*}[tb!]
  \centering
  \subfigure[\sys{} Versus LRC-BQ.]{
    \label{fig:10-a}
    \includegraphics[width=0.37\textwidth]{figures/precision-1.eps}}
  \hspace{0.6in}
   \subfigure[Various Data Items for \sys{}.]{
    \label{fig:11-a}
  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures-1.eps}}
  \caption{Performance of \sys{} }
\end{figure*}

>>>>

\par In this section, we shall first detail the experimental setting, and we then present the evaluation results and analyses, showing the benefit of \sys{} against state of the art approaches.

@@

\subsection{Results and Analyses}
Next, we shall report the performance of system \sys{} over each component.

@@

\stitle{Exp-2: User Clustering}
%
Fig.\ \ref{fig:10-c} depicts the Silhouette coefficient Values of multiple clustering solutions, with the cluster number varied from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users, and each of \textit{\{Data1,\ldots, Data5\}} contains 10K randomly selected users.
Except for \textit{Data1}, solutions for \textit{\{Data2,\ldots, Data5\}} are the best for 4 clusters.

@@

\begin{figure*}[tb!]
  \centering
  \subfigure[\sys{} Versus LRC-BQ.]{
    \label{fig:10-a}
    \includegraphics[width=0.37\textwidth]{figures/precision-2.eps}}
  \hspace{0.6in}
   \subfigure[Various Data Items for \sys{}.]{
    \label{fig:11-a}
  \includegraphics[width=0.45\textwidth]{figures/precisionofdifferentfeatures-1.eps}}
  \caption{Performance of \sys{} }
\end{figure*}

### 2018-02-25 DASFAA_2018/CR/Gruba_final/07-rela.tex

\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basics, behavior and interest.

@@

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis.
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Different from these existing solutions, \sys{} employs a cell lexicon to properly express user interests, in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.

Approaches of grouping users in social networks could fall into a variety of categories.
\cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc.
\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} studied the social groups on Facebook and Wechat, resulting various patterns of group evolution.
\cite{IEEEexample:conf/aaai/WangDNGEB16} proposed a time-varying factor to measure the affinity between users and groups such that proper group proposals are recommended.
More recent studies also look into mining user communities.
\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user community;
\cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering;
\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick.
Providing the diversity of user features, \sys{} employs basic, behavior and interest features into user clustering.

>>>>

\par In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behaviors within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basics, behavior and interest.

@@

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain user interests.
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtags for interest analysis.
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Different from these existing solutions, \sys{} employs a cell lexicon to properly express user interests, in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.

Approaches of grouping users in social networks could fall into a variety of categories.
\cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc.
\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} studied the social groups on Facebook and Wechat, resulting various patterns of group evolution.
\cite{IEEEexample:conf/aaai/WangDNGEB16} proposed a time-varying factor to measure the affinity between users and groups such that proper group proposals are recommended.
More recent studies also look into mining user communities.
\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user communities;
\cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering;
\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user communities using modular degree as the clustering yardstick.
Providing the diversity of user features, \sys{} employs basic, behavior and interest features into user clustering.
